\documentclass[letterpaper,11pt]{article}\usepackage{latexsym}\usepackage[empty]{fullpage}\usepackage{titlesec}\usepackage{marvosym}\usepackage[usenames,dvipsnames]{color}\usepackage{verbatim}\usepackage{enumitem}\usepackage[hidelinks]{hyperref}\usepackage{fancyhdr}\usepackage[english]{babel}\usepackage{tabularx}\usepackage{fontawesome5}\usepackage{multicol}\setlength{\multicolsep}{-3.0pt}\setlength{\columnsep}{-1pt}\input{glyphtounicode}\pagestyle{fancy}\fancyhf{}\fancyfoot{}\renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth}{0pt}\addtolength{\oddsidemargin}{-0.6in}\addtolength{\evensidemargin}{-0.5in}\addtolength{\textwidth}{1.19in}\addtolength{\topmargin}{-.7in}\addtolength{\textheight}{1.4in}\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]\pdfgentounicode=1\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & \textbf{\small #2} \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & \textbf{\small #2} \\\end{tabular*}\vspace{-7pt}}\newcommand{\resumeItemListStart}{\begin{itemize}}\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}\begin{document}\begin{center}{\Huge \scshape Ishita Roy} \\ \vspace{1pt}\small \raisebox{-0.1\height}\faEnvelope\ \href{mailto:ishita.roy.bba25@nmims.edu.in}{ishita.roy.bba25@nmims.edu.in} ~  \raisebox{-0.1\height}\faPhone\ +91 9123456780 ~ \href{linkedin.com/in/ishitaroybba}{\raisebox{-0.2\height}\faLinkedin\ \underline{ishitaroybba}} ~ \href{}{}\vspace{-8pt}\end{center}\section{Professional Summary}Final-year BBA student at NMIMS, Mumbai, graduating in April 2025, seeking entry-level roles in business analysis, consulting, or digital marketing. Interned at Deloitte as a Business Analyst and at HDFC Bank, gaining experience in consulting, market research, and retail banking.\section{Technical Skills}\begin{itemize}[leftmargin=0.15in, label={}]\item \textbf{Programming Languages}{: SQL (Basic)}\item \textbf{Machine Learning Tools}{:}\item \textbf{Generative AI \& Agents}{:}\item \textbf{Data Analysis}{: MS Excel, Tableau}\item \textbf{Development Tools}{: MS PowerPoint}\item \textbf{Soft Skills}{: Communication, Teamwork, Leadership, Event Organization}\end{itemize}\section{Experience}\resumeSubHeadingListStart\resumeSubheading{Business Analyst Intern}{June - August 2024}{Deloitte}{Mumbai}\resumeItemListStart\resumeItem{Worked with the consulting team on client projects.}\resumeItem{Prepared client reports and market research presentations.}\resumeItem{Assisted in a digital transformation strategy for a logistics company.}\resumeItemListEnd\resumeSubHeadingListEnd\resumeSubHeadingListStart\resumeSubheading{Campus Intern}{}{HDFC Bank}{}\resumeItemListStart\resumeItem{Learned about customer onboarding processes.}\resumeItem{Gained experience in KYC processes in the retail banking department.}\resumeItemListEnd\resumeSubHeadingListEnd\section{Projects}\resumeSubHeadingListStart\resumeProjectHeading{\textbf{Consumer Behavior and Online Shopping Trends Post-COVID} \$|\$ \emph{Excel, Charts}}{}\resumeItemListStart\resumeItem{Collected survey data on consumer behavior post-COVID.}\resumeItem{Analyzed data using Excel and charts to identify online shopping trends.}\resumeItemListEnd\resumeSubHeadingListEnd\section{Achievements}\resumeSubHeadingListStart\resumeItem{\textbf{Vice President, Entrepreneurship Cell} (): Organized events like business pitch competitions.}\resumeSubHeadingListEnd\section{Certifications}\resumeSubHeadingListStart\resumeItem{\textbf{Digital Marketing Certification}: Google}\resumeSubHeadingListEnd\section{Education}\resumeSubHeadingListStart\resumeSubheading{NMIMS}{April 2025}{BBA in Business Administration; \textbf{8.2/10 CGPA}}{Mumbai}\resumeSubHeadingListEnd\end{document}